PANCHANGE_analysis

### 2020-08-20 PANCHANGE_analysis.Rmd
sum scores for pcl, gad, phq, and ocir

@@

@@

@@

```{r descriptives phq.diff_score_cols}
phq.numeric_table <- dat %>% 
  #  group_by(dem.sex) %>%
  summarise_at( 
    vars(
      "Base - prepan" = phq.diff_score_base_prepan,
      "Base - retro" = phq.diff_score_base_retro,
      "Prepan - retro" = phq.diff_score_prepan_retro,
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )

@@

@@

@@

```{r descriptives pcl.diff_score_cols}
pcl.numeric_table <- dat %>% 
#    group_by(Sample) %>%
  summarise_at( 
    vars(
      "Prepan" = pcl.sum_score_prepan,
      "Base" = pcl.sum_score_base
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )

@@

>>>>

### Summary scores
```{r descriptives gad.diff_score_cols}
gad.sum_score_numeric_table <- dat %>% 
  #    group_by(Sample) %>%
  summarise_at( 
    vars(
      "Prepan" = gad.sum_score_prepan,
      "Base" = gad.sum_score_base,
      "Retro" = gad.sum_score_retro
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )

gad.sum_score_numeric_table
```

```{r smart numeric summary tables}
# reshape the table
gad.sum_score_numeric_summary_table_reshaped <- gad.sum_score_numeric_table %>% 
  gather(key, value) %>% 
  separate(key, c("variable", "measure"), sep = "_") %>%
  mutate(measure = factor(
    x = measure,
    levels =  c( # this is the order I want my columns to appear in
      "missing",
      "min",
      "max",
      "mean", 
      "median", 
      "mode",
      "sd",
      "skew",
      "kurtosis"
    ))) %>% 
  spread(measure, value) %>% 
  # we can apply a function to all variables to edit them so that they are publication ready
  rename_all(
    .funs = ~str_to_title(.)
  ) %>% 
  # or we can individually rename variables 
  rename(
    SD = Sd
  )

gad.sum_score_numeric_summary_table_reshaped
```

Table for knitting
gad diff summary table
```{r gad diff summary table}
kable(gad.sum_score_numeric_summary_table_reshaped)
```

### Differences scores

@@

### Long format

@@

### Plots

@@

### Summary scores
```{r descriptives phq.diff_score_cols}
phq.sum_score_numeric_table <- dat %>% 
  #    group_by(Sample) %>%
  summarise_at( 
    vars(
      "Prepan" = phq.sum_score_prepan,
      "Base" = phq.sum_score_base,
      "Retro" = phq.sum_score_retro
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )

phq.sum_score_numeric_table
```

```{r smart numeric summary tables}
# reshape the table
phq.sum_score_numeric_summary_table_reshaped <- phq.sum_score_numeric_table %>% 
  gather(key, value) %>% 
  separate(key, c("variable", "measure"), sep = "_") %>%
  mutate(measure = factor(
    x = measure,
    levels =  c( # this is the order I want my columns to appear in
      "missing",
      "min",
      "max",
      "mean", 
      "median", 
      "mode",
      "sd",
      "skew",
      "kurtosis"
    ))) %>% 
  spread(measure, value) %>% 
  # we can apply a function to all variables to edit them so that they are publication ready
  rename_all(
    .funs = ~str_to_title(.)
  ) %>% 
  # or we can individually rename variables 
  rename(
    SD = Sd
  )

phq.sum_score_numeric_summary_table_reshaped
```

Table for knitting
phq diff summary table
```{r phq diff summary table}
kable(phq.sum_score_numeric_summary_table_reshaped)
```

### Differences score

```{r descriptives phq.diff_score_cols}
phq.numeric_table <- dat %>% 
  #  group_by(dem.sex) %>%
  summarise_at( 
    vars(
      "Base - prepan" = phq.diff_score_base_prepan,
      "Base - retro" = phq.diff_score_base_retro,
      "Prepan - retro" = phq.diff_score_prepan_retro
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )

@@

### Summary scores
```{r descriptives ocir.diff_score_cols}
ocir.sum_score_numeric_table <- dat %>% 
  #    group_by(Sample) %>%
  summarise_at( 
    vars(
      "Prepan" = ocir.sum_score_prepan,
      "Base" = ocir.sum_score_base,
      "Retro" = ocir.sum_score_retro
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )

ocir.sum_score_numeric_table
```

```{r smart numeric summary tables}
# reshape the table
ocir.sum_score_numeric_summary_table_reshaped <- ocir.sum_score_numeric_table %>% 
  gather(key, value) %>% 
  separate(key, c("variable", "measure"), sep = "_") %>%
  mutate(measure = factor(
    x = measure,
    levels =  c( # this is the order I want my columns to appear in
      "missing",
      "min",
      "max",
      "mean", 
      "median", 
      "mode",
      "sd",
      "skew",
      "kurtosis"
    ))) %>% 
  spread(measure, value) %>% 
  # we can apply a function to all variables to edit them so that they are publication ready
  rename_all(
    .funs = ~str_to_title(.)
  ) %>% 
  # or we can individually rename variables 
  rename(
    SD = Sd
  )

ocir.sum_score_numeric_summary_table_reshaped
```

Table for knitting
ocir diff summary table
```{r ocir diff summary table}
kable(ocir.sum_score_numeric_summary_table_reshaped)
```

### Differences scores

@@

# RUBBISH

@@

```{r descriptives pcl.diff_score_cols}
pcl.sum_score_numeric_table <- dat %>% 
#    group_by(Sample) %>%
  summarise_at( 
    vars(
      "Prepan" = pcl.sum_score_prepan,
      "Base" = pcl.sum_score_base
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )

@@

```{r smart numeric summary tables}
# reshape the table
pcl.sum_score_numeric_summary_table_reshaped <- pcl.sum_score_numeric_table %>% 
  gather(key, value) %>% 
  separate(key, c("variable", "measure"), sep = "_") %>%
  mutate(measure = factor(
    x = measure,
    levels =  c( # this is the order I want my columns to appear in
      "missing",
      "min",
      "max",
      "mean", 
      "median", 
      "mode",
      "sd",
      "skew",
      "kurtosis"
    ))) %>% 
  spread(measure, value) %>% 
  # we can apply a function to all variables to edit them so that they are publication ready
  rename_all(
    .funs = ~str_to_title(.)
  ) %>% 
  # or we can individually rename variables 
  rename(
    SD = Sd
  )

pcl.sum_score_numeric_summary_table_reshaped
```

Table for knitting
pcl diff summary table
```{r pcl diff summary table}
kable(pcl.sum_score_numeric_summary_table_reshaped)
```
